\documentclass[a4paper,11pt]{article}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{titlesec}

\geometry{margin=0.75in}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\bfseries}{}{0em}{}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}

\title{\vspace{-2cm}\Huge Curriculum Vitae}
\author{\Large Nandini Chikkatumbal}
\date{}

\begin{document}
\maketitle

%---------------- CONTACT ----------------%
\section*{\textbf{Contact Information}}
\begin{itemize}[leftmargin=*]
    \item \textbf{Phone:} \href{tel:+918197220145}{+91-8197220145} \hfill \textbf{Email:} \href{mailto:nandininc97@gmail.com}{nandininc97@gmail.com}
    
    \item \textbf{GitHub:} \href{https://github.com/nandininc}{github.com/nandininc} \hfill \textbf{LinkedIn:} \href{https://www.linkedin.com/in/nandininc/}{linkedin.com/in/nandininc}
    
    \item \textbf{Portfolio:} \href{https://nandininc.netlify.app/}{nandininc.netlify.app}
\end{itemize}

%---------------- SUMMARY ----------------%
\section*{\textbf{Professional Summary}}

\textbf{Java Full Stack Developer} with \textbf{3+ years of experience} in designing and developing scalable enterprise applications using \textbf{Java, Spring Boot, React, Next.js, and PostgreSQL}. Strong expertise in \textbf{REST APIs, RBAC, authentication systems, workflow automation, CMS platforms, and performance optimization}. Experienced in complete \textbf{SDLC lifecycle}, API integration, responsive UI development, and deploying production-ready applications.

%---------------- SKILLS ----------------%
\section*{\textbf{Technical Skills}}

\begin{itemize}[leftmargin=*]
    \item \textbf{Programming Languages:} Java, JavaScript
    \item \textbf{Frameworks \& Libraries:} Spring Boot, React.js, Next.js
    \item \textbf{Frontend Technologies:} HTML5, CSS3, Tailwind CSS, Bootstrap
    \item \textbf{Databases:} MySQL, PostgreSQL
    \item \textbf{Tools \& Platforms:} Git, Linux, VS Code, Eclipse, Postman
    \item \textbf{Concepts:} REST APIs, GraphQL, RBAC, Authentication \& Authorization, PDF Generation, SSR, SSG
\end{itemize}

%---------------- EXPERIENCE ----------------%
\section*{\textbf{Professional Experience}}

%---------------- SWAJYOT ----------------%
\subsection*{\textbf{Java Full Stack Developer | Swajyot Technologies Pvt Ltd, Bangalore}}
\textit{March 2025 – Present}

\begin{itemize}[leftmargin=*]

    \item \textbf{AGI Green Pack – Document Management System}
    \begin{itemize}
        \item Designed and developed a secure \textbf{Document Management System} using \textbf{Spring Boot} and \textbf{React}.
        \item Implemented \textbf{multi-level approval workflows}, \textbf{RBAC}, and secure \textbf{document locking} mechanisms.
        \item Built dynamic forms with validations for structured business data capture.
        \item Integrated automated \textbf{PDF generation} for reporting and document workflows.
        \item Developed responsive dashboards and API-driven modules for workflow tracking.
    \end{itemize}

    \item \textbf{Headless CMS Content Portal – Swajyot Website}
    \begin{itemize}
        \item Independently designed and developed a \textbf{Headless CMS platform} using \textbf{Payload CMS}, \textbf{Next.js}, and \textbf{PostgreSQL}.
        \item Built dynamic content management modules for blogs, services, pages, SEO, and media management.
        \item Designed and integrated \textbf{REST} and \textbf{GraphQL APIs}.
        \item Implemented secure \textbf{authentication} and \textbf{Role-Based Access Control (RBAC)}.
        \item Optimized application performance using \textbf{SSR (Server-Side Rendering)} and \textbf{SSG (Static Site Generation)}.
        \item Managed end-to-end development including architecture, deployment, database setup, and production optimization.
    \end{itemize}

    \item \textbf{GageFxs – Calibration Management System}
    \begin{itemize}
        \item Developed a calibration management system for tracking industrial equipment calibration schedules and workflows.
        \item Implemented calibration due tracking, history logs, dashboards, notifications, and challan management.
        \item Built modules for service provider management and calibration workflow monitoring.
        \item Developed responsive UI components with backend API integration using React.
        \item Optimized rendering, pagination, and API handling for large datasets and historical records.
    \end{itemize}

\end{itemize}

%---------------- TECHFORTUNE ----------------%
\subsection*{\textbf{Java Full Stack Developer | TechFortune, Bangalore}}
\textit{April 2023 – February 2025}

\begin{itemize}[leftmargin=*]

    \item \textbf{LMS E-Learning Platform}
    \begin{itemize}
        \item Built a scalable \textbf{Learning Management System (LMS)} using \textbf{Spring Boot, React, and MySQL}.
        \item Implemented modules for \textbf{authentication, course management, quizzes, assignments, and student tracking}.
        \item Designed and developed secure and scalable \textbf{REST APIs} for frontend-backend integration.
        \item Developed responsive UI components and dashboard modules using React.
        \item Worked on user role management, validations, and performance optimization.
    \end{itemize}

\end{itemize}

%---------------- INTERNSHIP ----------------%
\subsection*{\textbf{Java Full Stack Intern | Palle Technologies, Bangalore}}
\textit{September 2022 – March 2023}

\begin{itemize}[leftmargin=*]
    \item Completed internship training focused on \textbf{Java Full Stack Development}.
    \item Developed mini-projects using \textbf{Java, Spring Boot, React, MySQL}, and REST APIs.
    \item Worked on frontend-backend integration and CRUD-based applications.
\end{itemize}

%---------------- TRAINING ----------------%
\subsection*{\textbf{Java Full Stack Trainee | Capgemini SHE ARISE Program}}
\textit{January 2022 – July 2022}

\begin{itemize}[leftmargin=*]
    \item Successfully completed intensive \textbf{6-month Java Full Stack training program}.
    \item Gained hands-on experience in \textbf{Core Java, Spring Boot, SQL, HTML, CSS, JavaScript, and React}.
    \item Built training projects and learned enterprise software development practices.
\end{itemize}

%---------------- PROJECTS ----------------%
\section*{\textbf{Projects}}

\begin{itemize}[leftmargin=*]

    \item \textbf{LMS E-Learning Platform}
    \begin{itemize}
        \item Built a scalable learning management system using \textbf{Spring Boot, React, and MySQL}.
        \item Implemented authentication, course management, quizzes, and student tracking modules.
        \item Designed secure and scalable REST APIs for frontend integration.
    \end{itemize}

    \item \textbf{Portfolio \& Blogging Websites}
    \begin{itemize}
        \item Developed responsive portfolio and blogging platforms with modern UI design principles.
    \end{itemize}

    \item \textbf{Face Mask Detection System}
    \begin{itemize}
        \item Built an AI-based face mask detection system using \textbf{TensorFlow} and \textbf{Keras}.
    \end{itemize}

    \item \textbf{Resort Booking Website}
    \begin{itemize}
        \item Developed a responsive resort booking website using \textbf{WordPress}. \\
        \textbf{\href{https://sanjeevtourism.com/}{https://sanjeevtourism.com/}}
    \end{itemize}

\end{itemize}

%---------------- EDUCATION ----------------%
\section*{\textbf{Education}}

\begin{itemize}[leftmargin=*]
    \item \textbf{Bachelor of Engineering (Computer Science Engineering)} \\
    KLS Vishwanathrao Deshpande Institute of Technology, Haliyal \\
    Passed Out: August 2021 \hfill CGPA: \textbf{8.2/10}
\end{itemize}

%---------------- CERTIFICATIONS ----------------%
\section*{\textbf{Certifications}}

\begin{itemize}[leftmargin=*]
    \item Java Full Stack Developer – Palle Technologies
    \item Capgemini SHE ARISE – Java Full Stack Training Program
\end{itemize}

%---------------- TEACHING ----------------%
\section*{\textbf{Teaching Experience}}

\subsection*{\textbf{Java Instructor | Besant Technologies, Bangalore}}
\textit{6 Months}

\begin{itemize}[leftmargin=*]
    \item Delivered Java and Full Stack Development training with practical coding sessions.
    \item Mentored students in Java, Spring Boot, React, and project development.
\end{itemize}

\end{document}